### 2016-01-12 branches/kevin-1397/docs/devel.tex
Add eature branch
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2811 40876441-3496-0410-a613-a2fca35b2ae2

The top level ludwig directory should contain at least the following:
\begin{lstlisting}
$ ls
bash-3.2$ ls
LICENSE         docs            src             tests           version.h
README          mpi_s           targetDP        util
\end{lstlisting}
The code is released under a standard BSD license; the current version
number is found in \texttt{version.h}. The main source is found in
the \texttt{src} directory, with other relevant code in \texttt{tests}
and \texttt{util}. The \texttt{targetDP} directory holds code related
to the targetDP abstraction layer \cite{gray2013}. These documents are
found in \texttt{docs}.

@@

The code is ANSI C (1999), and can be built without any external
dependencies, with the exception of the message passing interface
(MPI), which is used to provide domain-decomposition based parallelism.

@@

Compilation of the main code is controlled by the \texttt{Makefile} in
the \texttt{./src} directory. This section discusses a number of issues
which influence compilation.

@@

The \texttt{Makefile} provided in the source directory has a number of
targets to allow different models to be compiled. Before compilation,
the Makefile must be edited provide details of the local C compiler(s).
The relevant lines are usually limited to:
\begin{lstlisting}
CC = cc
MPICC = mpicc
CFLAGS = -O2
\end{lstlisting}
where \texttt{CC} is the compiler used for serial compilation,
\texttt{MPICC} is the compiler used for compilation against
MPI, and \texttt{CFLAGS} provides compiler switches (often
related to optimisation). Beyond these variables, changes to
the \texttt{Makefile} should not usually be required.

@@

The code makes quite a lot of use of standard C assertions, which
are useful to prevent errors. They do result in a considerably
slower execution in some instances, so production runs should
switch off the assertions with the standard \texttt{NDEBUG}
preprocessor flag. Add \texttt{-DNDEBUG} to \texttt{OPTS} in
the \texttt{Makefile}.

@@

A number of different scripts are provided for running serial, parallel,
or GPU tests. For each test script, there is the option to run either
the relevant unit tests, or regression tests, or both. For example, to
run both serial unit tests and serial regression tests for the D3Q19
model, invoke
\begin{lstlisting}
./test-serial.sh -u -r d3q19
\end{lstlisting}
in the test directory.
The model selection follows the naming scheme described for compilation
in the previous section.
See the individual scripts for further information on the command line
options.

>>>>

The top level ludwig directory should contain at least the following:
\begin{lstlisting}
$ ls
bash-3.2$ ls
config  LICENSE      mpi_s   src       tests  version.h
docs    Makefile.mk  README  targetDP  util
\end{lstlisting}
The code is released under a standard BSD license; the current version
number is found in \texttt{version.h}. The main source is found in
the \texttt{src} directory, with other relevant code in \texttt{tests}
and \texttt{util}. The \texttt{targetDP} directory holds code related
to the targetDP abstraction layer \cite{gray2013}. These documents are
found in \texttt{docs}.

@@

The code is ANSI C (1999), and can be built without any external
dependencies, with the exception of the message passing interface
(MPI), which is used to provide domain-decomposition based parallelism.
Note that the code will also compile under NVIDIA \texttt{nvcc}, i.e.,
it also meets the C++ standard.

@@

Compilation of the main code is controlled by the \texttt{config.mk} in
the  top-level directory. A number of example \texttt{config.mk} files
are provided in the \texttt{config} directory (which can be copied and
adjusted as needed). This section discusses a number of issues
which influence compilation.

@@

The \texttt{Makefile.mk} and \texttt{config.mk} files in the top level
directory control options for compilation. Before compilation,
the \texttt{config.mk} file must be edited provide details of the local
C compiler(s). The relevant lines are usually limited to, e.g.:
\begin{lstlisting}
CC = cc
MPICC = mpicc
CFLAGS = -O2
\end{lstlisting}
where \texttt{CC} is the compiler used for serial compilation,
\texttt{MPICC} is the compiler used for compilation against
MPI, and \texttt{CFLAGS} provides compiler switches (often
related to optimisation).

The \texttt{Makefile} provided in each subdirectory includes
the \texttt{config.mk} file via the top level \texttt{Makefile.mk}.
Changes to the individual Makefiles should therefore not be required.

If GPU compilation is required, the \texttt{config.mk} file should
specify the local details concerning \texttt{nvcc}. This includes
explicit information on the location of MPI headers and libraries
if an MPI-parallel GPU version is required.

@@

The code makes quite a lot of use of standard C assertions, which
are useful to prevent errors. They do result in a considerably
slower execution in some instances, so production runs should
switch off the assertions with the standard \texttt{NDEBUG}
preprocessor flag. Add \texttt{-DNDEBUG} to \texttt{CFLAGS} in
the \texttt{config.mk}.

@@

A number of different \texttt{Makefile} targets are provided for
running serial, parallel,
or GPU tests. For each test, there is the option to run either
the relevant unit tests, or regression tests, or both. For example, to
run both serial unit tests and serial regression tests for the D3Q19
model, invoke
\begin{lstlisting}
$ cd tests
$ make compile-run-serial
\end{lstlisting}
in the test directory.
The model selection follows the naming scheme described for compilation
in the previous section.

### 2016-01-12 branches/kevin-1397/targetDP/doc/memory_management.tex
Add eature branch
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2811 40876441-3496-0410-a613-a2fca35b2ae2

\chapter{Memory Management}

@@

\subsection{Syntax}
\begin{verbatim}
void targetMalloc(void **targetPtr, size_t n);
\end{verbatim}

@@

The \verb+targetCalloc+ function allocates, and initializes to zero, memory on the target.

\subsection{Syntax}
\begin{verbatim}
void targetCalloc(void **targetPtr, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void targetFree(void *targetPtr);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTarget(void *targetData, const void *data, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTarget(void *data, const void *targetData, size_t n);
\end{verbatim}

@@

\begin{itemize}
\item \verb+variableName+: The name of the variable or array.
\item \verb+type+: The type of variabe or array.
\end{itemize}

@@

\subsection{Syntax}
\begin{verbatim}
void copyConstToTarget(void *targetData, const void *data, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void targetConstAddress(void **address, objectType object);
\end{verbatim}

@@

The \verb+targetInit3D+ initialises the environment required to perform any of following the targetDP 3D lattice operations.

@@

The \verb+targetFinalize3D+ finalizes the targetDP 3D environment.

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTargetBoundary3D(void *targetData, const void *data, size_t extent3D[3], size_t nField, size_t offset, size_t depth);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTargetBoundary3D(void *data, const void *targetData, size_t extent3D[3], size_t nField, size_t offset, size_t depth);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTargetPointerMap3D(void *targetData, const void *data, 
           size_t extent3D[3], size_t nField, 
           int includeNeighbours, void** pointerArray);
\end{verbatim}

\begin{itemize}
\item \verb+targetData+: A pointer to the destination array on the target.
\item \verb+data+: A pointer to the source array on the host.
\item \verb+extent3D+: An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+nField+: The number of fields per lattice site.
\item \verb+includeNeighbours+: A boolean switch to specify whether each included site should also have it's neighbours included (in the 19-point 3D stencil).
\item \verb+pointerArray+: An array of \verb+nSite+ pointers, where \verb+nSite+ is the total number of lattice sites. Each lattice site should be included unless the pointer corresponding to that site is \verb+NULL+.  
\end{itemize}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTargetPointerMap3D(void *data, const void *targetData, 
           size_t extent3D[3], size_t nField, 
           int includeNeighbours, void** pointerArray);
\end{verbatim}

\begin{itemize}
\item \verb+data+: A pointer to the destination array on the host.
\item \verb+targetData+: A pointer to the source array on the target.
\item \verb+extent3D+: An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+nField+: The number of fields per lattice site.
\item \verb+includeNeighbours+: A boolean switch to specify whether each included site should also have it's neighbours included (in the 19-point 3D stencil).
\item \verb+pointerArray+: An array of \verb+nSite+ pointers, where \verb+nSite+ is the total number of lattice sites. Each lattice site should be included unless the pointer corresponding to that site is \verb+NULL+.  
\end{itemize}

>>>>

\chapter{Memory Management}\label{chap:memmanage}

@@

\subsection{Syntax}
\begin{verbatim}
void targetMalloc(void** targetPtr, size_t n);
\end{verbatim}

@@

The \verb+targetCalloc+ function allocates, and initialises to zero, memory on the target.

\subsection{Syntax}
\begin{verbatim}
void targetCalloc(void** targetPtr, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void targetFree(void* targetPtr);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTarget(void* targetData, const void* data, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTarget(void* data, const void* targetData, size_t n);
\end{verbatim}

@@

\begin{itemize}
\item \verb+variableName+: The name of the variable or array.
\item \verb+type+: The type of variable or array.
\end{itemize}

@@

\subsection{Syntax}
\begin{verbatim}
void copyConstToTarget(void* targetData, const void* data, size_t n);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void targetConstAddress(void** address, objectType object);
\end{verbatim}

@@

The \verb+targetInit3D+ initialises the environment required to perform any of the ``3D'' operations described in the rest of this chapter.

@@

The \verb+targetFinalize3D+ finalises the targetDP 3D environment.

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTargetBoundary3D(void* targetData, const void* data, 
              size_t extent3D[3], size_t nField, 
              size_t offset, size_t depth);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTargetBoundary3D(void* data, const void* targetData, 
                 size_t extent3D[3], size_t nField, 
                 size_t offset, size_t depth);
\end{verbatim}

@@

\subsection{Syntax}
\begin{verbatim}
void copyToTargetPointerMap3D(void* targetData, const void* data, 
           size_t extent3D[3], size_t nField, 
           int includeNeighbours, void** pointerArray);
\end{verbatim}

\begin{itemize}
\item \verb+targetData+: A pointer to the destination array on the target.
\item \verb+data+: A pointer to the source array on the host.
\item \verb+extent3D+: An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+nField+: The number of fields per lattice site.
\item \verb+includeNeighbours+: A Boolean switch to specify whether each included site should also have it's neighbours included (in the 19-point 3D stencil).
\item \verb+pointerArray+: An array of \verb+nSite+ pointers, where \verb+nSite+ is the total number of lattice sites. Each lattice site should be included unless the pointer corresponding to that site is \verb+NULL+.  
\end{itemize}

@@

\subsection{Syntax}
\begin{verbatim}
void copyFromTargetPointerMap3D(void* data, const void* targetData, 
           size_t extent3D[3], size_t nField, 
           int includeNeighbours, void** pointerArray);
\end{verbatim}

\begin{itemize}
\item \verb+data+: A pointer to the destination array on the host.
\item \verb+targetData+: A pointer to the source array on the target.
\item \verb+extent3D+: An array of 3 integers corresponding to the 3D dimensions of the lattice.
\item \verb+nField+: The number of fields per lattice site.
\item \verb+includeNeighbours+: A Boolean switch to specify whether each included site should also have it's neighbours included (in the 19-point 3D stencil).
\item \verb+pointerArray+: An array of \verb+nSite+ pointers, where \verb+nSite+ is the total number of lattice sites. Each lattice site should be included unless the pointer corresponding to that site is \verb+NULL+.  
\end{itemize}
